---
title: "First R markdown file"
author: "Jessica Cole"
date: "September 4, 2018"
output:
  html_document: 
    highlight: tango
    number_sections: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hello world!   What happens to funny spacing?        Is it preserved?

First line.   
Second line.   
Third line.    

italic *this way*

bold face **like this**

subscript~lower~

superscript^raised^

strikethrough ~~for mistakes~~

# First Level

## Second Level

###Third Level

...

######Six Level!


lists are easy

- first item
- second item
- third item, and yes it will keep everything aligned just as it shuld be for longer text!
    - subitem
        - sub-subitem
        
>All musicians are subconsciously matemiticians

Thelonious Monk

Use single bactick for in-line emphasis `  like this`.

Shows literal text as `3 + pi`.

Start with r to get it to run r code this `r 3 + pi`. 


### Code fencing

```
# Comments are important!
pred <- seq(1,10) # make a vector of intergers from one to 10
response <- runif(10)
print(response)

# now plot a graph
plot(x=pred,
     y=response,
     type="b")
```

```{r, eval=FALSE, echo=TRUE}
# Comments are important!
pred <- seq(1,10) # make a vector of intergers from one to 10
response <- runif(10)
print(response)

# now plot a graph
plot(x=pred,
     y=response,
     type="b")
```
     

## Creating equations with`LaTex`

An `inline` equations is bracketed by single dollar signs $3 + 5 = 8$ like this.

For more complex equations, we will render them on a single line by using a double dollar sign to bracket them:

$$3 + 5 = 8$$

Keeps this as a stand-alone piece.

Subscripts as follows:

$$H_0 = Z_{a + b_{3z}}$$