---
title: "Simulating and Fitting Data Distributions"
author: "Jessica Cole"
date: "October 3, 2018"
output: html_document
---

```{r}
# open libraries
library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

# read in data vector
#z <- rnorm(n=3000,mean=0.2)
#z <- data.frame(1:3000,z)
#names(z) <- list("ID","myVar")
#z <- z[z$myVar>0,]
#str(z)
#summary(z$myVar)

z <- read.table("catsM.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)
names(z) <- list("ID","myVar")
str(z)
summary(z)

# Plot histogram of data - switching from qplot to ggplot for more graphics options, also rescale the y axis
p1 <- ggplot(data=z, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)
# creating the graph based on the data

# adding empirical density curve - curve fitted to the data, does not assume any particular probability distribution, and smooths out the shape of the histogram
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)
# adds line over data

# get maximum likelihood parameters for normal(data?) - fit normal distribution to your data. Grabs the maximum likelihood estimators of the two parameters fo the normal, the mean and variance
normPars <- fitdistr(z$myVar,"normal")
print(normPars)
# gives mean and standard deviation
str(normPars)
normPars$estimate["mean"] # note structure of getting a named attribute

#plot normal probability density, dnorm function generates the probability density for the normal distribution
#fitdistr gives maximum likelihood parameters for a normal distribution fitted to the data
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]
# gives mean again but rounds next to last number up

xval <- seq(0,max(z$myVar),len=length(z$myVar))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$myVar), args = list(mean = meanML, sd = sdML))
 p1 + stat
 # gives red line <- gives normal distriubution
 
# plot exponential probability density - add in the curve for the exponential
 expoPars <- fitdistr(z$myVar,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$myVar), args = list(rate=rateML))
 p1 + stat + stat2
 # give blue line <- exponential probability distribution
 
 # Plot uniform probability density - 
 stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$myVar), args = list(min=min(z$myVar), max=max(z$myVar)))
 p1 + stat + stat2 + stat3
 # gives green line <- uniform distribution
 
 # Plot gamma probability density
 gammaPars <- fitdistr(z$myVar,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$myVar), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
 # gives brown line <- gamma distribution
 
 # plot beta probability density
 pSpecial <- ggplot(data=z, aes(x=myVar/(max(myVar + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$myVar/max(z$myVar + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$myVar), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial
# gives pink line <- beta distribution

normPars <- fitdistr(z$myVar,"gamma")
print(normPars)
# Plot gamma probability density
 gammaPars <- fitdistr(z$myVar,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$myVar), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4



shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]
```
Gamma distribution seems to be the best probability distribution for the specific data set. The heart weight was used as the continuous variables.


```{r}
# simulated data
simheartmass <- rgamma(97, 20.36202, rate = 1.79834)
print(simheartmass)
simheartmass <- data.frame(id=1:97,myVar=simheartmass)
p1 <- ggplot(data=simheartmass, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)
```

```{r}
library(ggplot2) # for graphics
library(MASS)

z <- read.table("catsM.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)
names(z) <- list("ID","myVar")
str(z)
summary(z)
p1 <- ggplot(data=z, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)

```

The simulation data graph is similar to the original data. The extremes are still present in both graphs, extending the empiral data line. However, the data in the similuated graph is slightly different with less identical variants.
